Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-10-30 ms/ms.Rmd
ms: add depthsByClass table

Include a 12cm width figure of Nikolaus Copernicus from [Wikipedia](https://en.wikipedia.org/wiki/File:Nikolaus_Kopernikus.jpg) with caption using R Markdown (Fig. \@ref(fig:portrait)).

```{r portrait, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("Nikolaus_Kopernikus.jpg")
```

## Tables

You can add \LaTeX table in an R Markdown document to meet the template requirements (Table \ref{tab:latextable}).

\begin{table}[t]
\caption{TEXT}
\begin{tabular}{l c r}
\tophline

a & b & c \\
\middlehline
1 & 2 & 3 \\

\bottomhline
\end{tabular}
\belowtable{Table Footnotes}
\label{tab:latextable}
\end{table}

Or you can use markdown to create the table with booktabs = FALSE (<https://github.com/rstudio/rticles/issues/558#issuecomment-1907981541>).

See Table \@ref(tab:test).

```{r test, echo=FALSE}
df = mtcars[1:3, 1:3]
knitr::kable(df, booktabs = FALSE, caption = "My caption")
```

>>>>

We obtained depth measurements for 372 cells (XX % of mapped peatland) at Skrimfjella and 1889 cells (XX % of mapped peatland) at Ørskogfjellet.
The mean depths of these \unit{10\,m} cells differed by only \unit{6\,cm} between Skrimfjella and Ørskogfjellet (Table \ref{tab:depthsByClass}).

\begin{table}[tbp]
\caption{Mean peat depth (cm) in \unit{10\,m} cells at Skrimfjella and Ørskogfjellet. The cells are also shown stratified by AR5 land class and DMK peat depth class.}
\begin{tabular}{llllllll}
\hline
    &                            & \multicolumn{3}{c}{Skrimfjella} & \multicolumn{3}{c}{Ørskogfjellet} \\ \cline{3-8} 
    &                            & n        & \%      & depth      & n          & \%      & depth      \\ \hline
    &                            & 372      & 100     & 119        & 1889       & 100     & 125        \\
AR5 & Fully cultivated           &          &         &            & 21         & 1       & 30         \\
    & Forest                     & 52       & 14      & 65         & 272        & 14      & 71         \\
    & Open firm ground           & 19       & 5       & 98         & 134        & 7       & 39         \\
    & Peatland                   & 301      & 81      & 130        & 1451       & 77      & 145        \\
DMK & deep (\textgreater 100 cm) & 94       & 25      & 100        & 659        & 35      & 219        \\
    & shallow (\textless 100 cm) & 6        & 2       & 50         & 839        & 44      & 82         \\
    & unknown                    & 272      & 73      & 127        & 391        & 21      & 59         \\ \hline
\end{tabular}
\label{tab:depthsByClass}
\end{table}

### 2024-10-30 ms/ms.tex
ms: add depthsByClass table

Include a 12cm width figure of Nikolaus Copernicus from \href{https://en.wikipedia.org/wiki/File:Nikolaus_Kopernikus.jpg}{Wikipedia} with caption using R Markdown (Fig. \ref{fig:portrait}).

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:portrait}
\end{figure}

\subsection{Tables}

You can add \LaTeX table in an R Markdown document to meet the template requirements (Table \ref{tab:latextable}).

\begin{table}[t]
\caption{TEXT}
\begin{tabular}{l c r}
\tophline

a & b & c \\
\middlehline
1 & 2 & 3 \\

\bottomhline
\end{tabular}
\belowtable{Table Footnotes}
\label{tab:latextable}
\end{table}

Or you can use markdown to create the table with booktabs = FALSE (\url{https://github.com/rstudio/rticles/issues/558\#issuecomment-1907981541}).

See Table \ref{tab:test}.

\caption{\label{tab:test}My caption}
\centering
\begin{tabular}[t]{l|r|r|r}
\hline
  & mpg & cyl & disp\\
\hline
Mazda RX4 & 21.0 & 6 & 160\\
\hline
Mazda RX4 Wag & 21.0 & 6 & 160\\
\hline
Datsun 710 & 22.8 & 4 & 108\\
\hline
\end{tabular}
\end{table}

>>>>

We obtained depth measurements for 372 cells (XX \% of mapped peatland) at Skrimfjella and 1889 cells (XX \% of mapped peatland) at Ørskogfjellet.
The mean depths of these \unit{10\,m} cells differed by only \unit{6\,cm} between Skrimfjella and Ørskogfjellet (Table \ref{tab:depthsByClass}).

\begin{table}[tbp]
\caption{Mean peat depth (cm) in \unit{10\,m} cells at Skrimfjella and Ørskogfjellet. The cells are also shown stratified by AR5 land class and DMK peat depth class.}
\begin{tabular}{llllllll}
\hline
    &                            & \multicolumn{3}{c}{Skrimfjella} & \multicolumn{3}{c}{Ørskogfjellet} \\ \cline{3-8} 
    &                            & n        & \%      & depth      & n          & \%      & depth      \\ \hline
    &                            & 372      & 100     & 119        & 1889       & 100     & 125        \\
AR5 & Fully cultivated           &          &         &            & 21         & 1       & 30         \\
    & Forest                     & 52       & 14      & 65         & 272        & 14      & 71         \\
    & Open firm ground           & 19       & 5       & 98         & 134        & 7       & 39         \\
    & Peatland                   & 301      & 81      & 130        & 1451       & 77      & 145        \\
DMK & deep (\textgreater 100 cm) & 94       & 25      & 100        & 659        & 35      & 219        \\
    & shallow (\textless 100 cm) & 6        & 2       & 50         & 839        & 44      & 82         \\
    & unknown                    & 272      & 73      & 127        & 391        & 21      & 59         \\ \hline
\end{tabular}
\label{tab:depthsByClass}
\end{table}
